Scaling up the hyperparameter grid for Naomi

### 2023-12-05 src/dev_scale-grid/scale-grid.Rmd
Improvements to PCA-AGHQ plots for thesis

ggsave("marginal-sd.png", height = 3.5, w = 6.25)
```

@@

```{r cov, class.source = 'fold-hide', fig.cap="Covariance matrix."}
C <- sd_out$cov.fixed
(C_plot <- plot_matrix(C))
```

@@

ggsave("pc-loadings.png", h = 3.5, w = 6.25)
```

@@

C_s_plot <- plot_matrix(C_s)
{C_plot + theme(legend.position = "none") + labs(subtitle = "Full rank")} + {C_s_plot + theme(legend.position = "none") + labs(subtitle = "Reduced rank")}

>>>>

ggsave("marginal-sd.png", height = 4, w = 6.25)
```

@@

```{r cov, class.source = 'fold-hide', fig.cap="Covariance matrix."}
C <- sd_out$cov.fixed
(C_plot <- plot_matrix(unname(C), legend = FALSE))
```

@@

ggsave("pc-loadings.png", h = 4.5, w = 6.25)
```

@@

C_s_plot <- plot_matrix(C_s, legend = FALSE)

{C_plot + labs(tag = "A", caption = "Full rank")} + {C_s_plot + labs(tag = "B", caption = "Reduced rank")}
